Verified Time Balancing of Security Protocols

### 2019-01-19 Src/talk.tex
some work fleshing out slides, just need to implement diagrams and practice speech

\begin{frame}[fragile]
  \frametitle{Quick Background 1 - Currying}
  All functions treated as taking a single argument. \\ \\
  $f : \mathbb{N} \rightarrow \mathbb{N} \rightarrow \mathbb{N}$ \\
  $f = + $ \\ \\
  Applying an argument to a multi argument function returns the 
  rest of the function! \\ \\
  $f(2) : \mathbb{N} \rightarrow \mathbb{N}$ \\
  $f(2) = 2 + $ \\ \\
  Finally all arguments are applied. \\ \\
  $f(2, 3) : \mathbb{N}$ \\
  $f(2, 3) = 2 + 3 = 5 $
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Quick Background 3 - Idris Syntax and Functions as Types}
  Building a vector type in Idris: 
  \begin{minted}{haskell}
    data Vec : Nat -> Type -> Type where
      Nil  : Vec 0 a
      (::) : (x : a) -> Vec n a -> Vec (n + 1) a
  \end{minted}
  We can parameterise types over values to capture invariants in the model.
  \begin{minted}{haskell}
    append : Vec n a -> Vec m a -> Vec (n + m) a
    append Nil ys = ys
    append (x :: xs) ys = x :: append xs ys 
  \end{minted}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Capturing time invariants in a small DSL}
  %insert picture for prg here!
\end{frame}

\end{document}

>>>>

\begin{frame}[fragile]
  \frametitle{Quick Background 1 - Currying}
  All functions treated as taking a single argument. \\ \\
  $f : \mathbb{N} \rightarrow \mathbb{N} \rightarrow \mathbb{N}$ \\
  $f = + $ \\ \\
  Applying an argument to a multi argument function returns the 
    rest of the function! (Arrow associates to the right)\\ \\
  $f(2) : \mathbb{N} \rightarrow \mathbb{N}$ \\
  $f(2) = 2 + $ \\ \\
  Finally all arguments are applied. \\ \\
  $f(2, 3) : \mathbb{N}$ \\
  $f(2, 3) = 2 + 3 = 5 $
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Quick Background 3 - Idris Syntax and Values as Types}
  Building a vector type in Idris: 
  \begin{minted}{haskell}
    data Vec : Nat -> Type -> Type where
      Nil  : Vec 0 a
      (::) : (x : a) -> Vec n a -> Vec (n + 1) a
  \end{minted}
  We can parameterise types over values to capture invariants in the model.
  \begin{minted}{haskell}
    append : Vec n a -> Vec m a -> Vec (n + m) a
    append Nil ys = ys
    append (x :: xs) ys = x :: append xs ys 
  \end{minted}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Capturing time invariants in a small DSL}
  %code for prg goes here, correct by construction
  \begin{minted}
  \end{minted}
\end{frame}

\begin{frame}[fragile]
  \frametitle{What about more expressive time parameters?}
  %discuss how in the case of mod, we can have the time parameter
  %expressed as a function of the input
\end{frame}

\begin{frame}[fragile]
  \frametitle{Elaboration and Compilation of a small correct core}
  %diagram on how a small correct core can be both elaborated and compiled
  %for compiled can be mapped to a specific chipset achitecture
\end{frame}

\begin{frame}[fragile]
  \frametitle{Contributions}
  \begin{itemize}
    \item Formal description of a simplified protocol.
    \item Prg: A small language parameterised over computational time
    \item Some small proofs of Prg correctness.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Further Work}
  \begin{itemize}
    \item Implement the simplified protocol in Prg.
    \item Modulo arithmetic cases.
    \item Relax some of the (many) assumptions.
    \item Investigate elaboration and compilation with regard to invariants.
  \end{itemize}
\end{frame}
\end{document}
